Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-04 main.tex
Added tikz picture of sensor subsets

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

>>>>

% Added operators
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% Tikz settings
\usetikzlibrary{math}

@@

\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
    % Sizes
    \tikzmath{\srange = 3.54; \sradius = 0.04;}
    % Sensor locations (sensor 3 is shared)
    \coordinate (s1) at (1.132,-4.4338);
    \coordinate (s2) at (4.0633,-5.9948);
    \coordinate (s3) at (3.1235,-3.2054);
    \coordinate (s4) at (4.5563,-1.6861);
    \coordinate (s5) at (5.9909,-3.5635);
    % Navigator location
    \coordinate (nav_loc) at (4,-4);
    % Bounding rectangle
    \coordinate (brect_start) at (0,0);
    \coordinate (brect_end) at (8.0, -8.0);

    % Gray range circles
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \draw[gray!50] (s1) circle (\srange);
        \draw[gray!50] (s2) circle (\srange);
        \draw[gray!50] (s3) circle (\srange);
        \draw[gray!50] (s4) circle (\srange);
        \draw[gray!50] (s5) circle (\srange);
    \end{scope}
    % Red subgroup overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s3) circle (\srange);
        \clip (s4) circle (\srange);
        \clip (s5) circle (\srange);
        \fill[red!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Blue subgroup overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s1) circle (\srange);
        \clip (s2) circle (\srange);
        \clip (s3) circle (\srange);
        \fill[blue!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Magenta double overlap
    \begin{scope}
        \clip (brect_start) rectangle (brect_end);
        \clip (s1) circle (\srange);
        \clip (s2) circle (\srange);
        \clip (s3) circle (\srange);
        \clip (s4) circle (\srange);
        \clip (s5) circle (\srange);
        \fill[magenta!40] (brect_start) rectangle (brect_end);
    \end{scope}
    % Sensors
    \fill[black] (s1) circle (\sradius);
    \fill[black] (s2) circle (\sradius);
    \fill[black] (s3) circle (\sradius);
    \fill[black] (s4) circle (\sradius);
    \fill[black] (s5) circle (\sradius);
    % Bounding box
    \draw[gray] (brect_start) rectangle (brect_end);
    % Navigator
    \clip (brect_start) rectangle (brect_end);
    \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
        % Plane
        \draw[fill]  plot[smooth, tension=.6] coordinates {
        (-0.65,-0.9) 
        (-0.6,-0.85) 
        (-0.4,-0.75) 
        (-0.25,-0.65) 
        (-0.15,-0.5) 
        (-0.12,-0.3) 
        (-0.10,-0.1) 
        (0.0,0.0) 
        (0.10,-0.1) 
        (0.12,-0.3) 
        (0.15,-0.5) 
        (0.25,-0.65) 
        (0.4,-0.75) 
        (0.6,-0.85) 
        (0.65,-0.9)
        } -- plot[smooth, tension=.6] coordinates {
        (0.65,-0.9) 
        (0.15,-0.91)
        (0.35,-1.1) 
        (0.37,-1.15)
        } -- plot[smooth, tension=.6] coordinates {
        (0.37,-1.15)
        (0.0,-1.12) 
        (-0.37,-1.15) 
        } -- plot[smooth, tension=.6] coordinates {
        (-0.37,-1.15)
        (-0.35,-1.1) 
        (-0.15,-0.91) 
        (-0.65,-0.9) 
        } -- cycle;
        % Trail
        \fill[bottom color=white, top color=gray] (-0.05, -1.5) rectangle (0.05, -50);
    \end{scope}
    \node[label=1] at (s1) {};
    \node[label=2] at (s2) {};
    \node[label=3] at (s3) {};
    \node[label=4] at (s4) {};
    \node[label=5] at (s5) {};
\end{tikzpicture}
\caption{Sensor subsets $\{1,2,3\}$ and $\{3,4,5\}$, and the areas within which the navigator is in range of all sensors within a subset.}
\label{fig:sensor_subsets}
\end{figure}
